QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added make target for running uk qaly scenarios on arc, and updated path in comparison scripts to uk scaled output directory

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'SF12_uk_scaled')

>>>>

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'SF12_uk_scaled')
